Supplement to Automatic Matching of Bullet Lands

### 2015-12-30 imaging-supplement.Rnw
up to stability.
crosscuts-sd.csv file and some discussion (In the supplement) added

\section{Cylindrical Fit}

@@

\subsection{Assessing cross-correlation between signatures at multiple cross sections}

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], lop[[4]], lop[[5]], lop[[6]],
             ncol = 2)
@
\caption{\label{fig:crosscuts}Overview of the variations in the surface along different cross sections. Cross section at $x = 100$ is compared to cross sections every 50$\mu m$. With every step away from the original cross section site, the number of differences between the cross sections increases, and the number of maximum CMS decreases from initially 14 to  3 or fewer at $x = 300\mu m$ and higher. }
\end{figure}
\end{document}

>>>>

\section{Cylindrical Fit}\label{supp:cylindrical}

@@

\section{Assessing cross-correlation between signatures at multiple cross sections}

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], lop[[4]], lop[[5]], lop[[6]],
             ncol = 2)
@
\caption{\label{fig:crosscuts}Overview of the variations in the surface along different cross sections. Cross section at $x = 100$ is compared to cross sections every 50$\mu m$. With every step away from the original cross section site, the number of differences between the cross sections increases, and the number of maximum CMS decreases from initially 14 to  3 or fewer at $x = 300\mu m$ and higher. }
\end{figure}

\section{Signature intensities}

\hh{XXX Overview of the signatures across one bullet land. Maybe with color?}

Standard deviation of signatures is one measure to quantify the extent to which they are expressed. Figure~\ref{fig:crosscuts} shows the amount of the standard deviation across crosscuts for all bullet lands shown as lines. Standard deviation decreases as the crosscut increases, i.e.\ bullets' signatures are most expressed close to the bottom of the bullet. \hh{XXX can we find an AFTE citation to back this up?}

\begin{figure}[hbtp]
\centering
<<crosscuts-sd, echo=FALSE, fig.height=5, fig.width=8, out.width='.7\\textwidth'>>=
if (!file.exists("csvs/crosscut-sd.csv")) {
  bullets_processed <- lapply(all_bullets, function(bul) {
    cat("Computing processed bullet", basename(bul$path), "\n")
    crosscuts <- 25*(1:20)
    dframe <- new_processBullets(bullet = bul, x = crosscuts)
    dframe$bullet <- with(dframe, paste(bullet, x))
    dframe
  })
  names(bullets_processed) <- as.character(ccs$path)

  bullets_smoothed <- bullets_processed %>% bind_rows %>% bulletSmooth

  stats <- bullets_smoothed %>% group_by(bullet, x) %>% summarize(
    sd = sd(l30, na.rm=T)
  )
  splits <- strsplit(stats$bullet, split=".", fixed=TRUE)
  bnames <- sapply(splits, function(x) paste(x[1],".x3p", sep=""))
  stats$bullet <- bnames

  write.csv(stats, "csvs/crosscut-sd.csv", row.names=FALSE)
} else {
  stats <- read.csv("csvs/crosscut-sd.csv")
}

qplot(x, sd, data=stats, geom="line", group=bullet, alpha=I(0.5)) + theme_bw() +
  geom_smooth(group=1) + 
  xlab("Crosscut location") +
  ylab("Standard deviation")
@
\caption{\label{fig:crosscuts}Standard deviation reduces as crosscut levels increase.}
\end{figure}

\end{document}
